% job listing environments

\newenvironment{jobshort}[4]{%
  \begin{tabularx}{\linewidth}{@{}X r@{}}
    \textbf{#1} & #4 \\[-1pt]
    \textit{#2, #3} & \\[3pt]
  \end{tabularx}
}{}

% joblong: Title, Institution, Location, Date
\newenvironment{joblong}[4]{%
  \begin{tabularx}{\linewidth}{@{}X r@{}}
    \textbf{#1} & #4 \\[-1pt]
    \textit{#2, #3} & \\[3pt]
  \end{tabularx}
  \begin{itemize}[leftmargin=1em, label=--,topsep=2pt, partopsep=3pt, parsep=0pt, itemsep=2pt]
}{%
  \end{itemize}
  \vspace{0.6em} % <-- add or adjust this (e.g., 0.5em–1em)
}


\section*{Experience}

\begin{joblong}{Medical Informatics PhD Candidate}{Biomedical AI Research}{Los Angeles}{September 2021 -- Present}
    \item Developing a scalable EEG foundation model trained on 50{,}000+ hours of data to capture temporal, spatial, and spectral neural representations.
    \item Investigating thalamocortical network mechanisms in pediatric epilepsy using SEEG spectral and connectivity analyses, generating insights for neuromodulation strategies.
    \item Designing multimodal learning techniques to relate EEG signals to gait metrics in Parkinson’s Disease, identifying neural features associated with gait impairment.
    \item Mentored a team of undergraduate students to develop a neural decoding and BCI motor-imagery pipeline integrating PyTorch, MNE, and BCI2000 for real-time experiments, resulting in a first-place award at UCLA Bioengineering Research Day.
\end{joblong}



\begin{joblong}{Research Scientist Intern}{Meta FAIR (BrainAI)}{London}{Mar 2025 - August 2025}
\item Developed large-scale foundation models for brain encoding and decoding within the Brain AI team.
\item Contributed to production-scale research codebases for multimodal neural data analysis.
\item Designed and evaluated model architectures for mapping neural activity to sensory and cognitive representations.
\end{joblong}




\begin{joblong}{Data Science Intern}{Dascena}{Remote}{March 2020 -- May 2022}
    \item Evaluated deep learning models to predict C. Diff infection in the ICU, resulting in a journal publication.
    \item Built predictive models using longitudinal EMR data for multiple clinical indications, resulting in 3 journal publications
    \item Developed EHR data processing pipelines using AWS and PySQL to enable analysis at scale.
\end{joblong}

% \begin{joblong}{Technical Operations Intern}{Vertex Pharmaceuticals}{Boston}{June 2019 -- August 2019}
%     \item Developed a data acquisition and analysis pipeline for continuous drug production data.
%     \item Built algorithms and a GUI for ETL and trend analysis on thousands of production reports.
%     \item Increased analysis speed by 500x using Tabula, Pandas, PyQt, SQL, and SEEQ.
% \end{joblong}

\begin{joblong}{Undergraduate Researcher}{Maharbiz Lab}{Berkeley}{January 2018 -- May 2020}
    \item Designed novel automations and experiments to evaluate neural implant biocompatibility in silico.
    \item Assembled automated accelerated aging experiments using Raspberry Pi, PySerial, and MATLAB, resulting in a conference publication.
\end{joblong}

% \begin{joblong}{Vice President of Projects}{Neurotech@Berkeley}{Berkeley}{January 2018 -- May 2021}
%     \item Developed a seamless EEG analysis and modeling platform for commercially available EEG devices.
%     \item Created a data science-based curriculum to make neurotechnology accessible to the public.
%     \item Built collaborations with neurotechnology research groups, leading to a student-led neurotech course at UC Berkeley.
% \end{joblong}
